Cleaning the data

### 2017-12-08 Analysis/data_cleaning.Rmd
cleaned data

## General
general <- c("Metazoans", "Ediacarian", "Marine invertebrates", "Amniotes", "Vertebrates")
data_taxa <- multi.gsub(general, "general", data_taxa)

@@

## Pairwise distance
pair_distances <- c("DTT \\(morpho evolution in relation to diversification\\)", "DTT pairwise Euclidean distance", "weighted mean pairwise dissimilarity", "pairwise euclidean distance", "DTT pairwise average squared Euclidean distance", "mean pairwise dissimilarity", "sum of squared pairwise distance between coordinates", " pairwise distance", "average pairwise disparity", "Average pairwise squared distance", "average pairwise dissimilarity", "mean square distance between sp", "distance between species", "pairwise character dissimilarity", "mean pairwise distance", "pairwise distance", "mean squared pairwise difference in body size", "average morphological dissimilarity", "Average pairwise dissimilarity", "Pairwise Mahalanobis distance", "sum of the absolute distance for each variable")
disparity <- multi.gsub(pair_distances, "pair_distances", disparity)

@@

## regressions
linear <- c("PGLS \\(PC \\~ trait\\)", "Partial Least Squares", "Canonical analysis \\(PCM style\\)", "lm", "Covariance ratio", "GLS", "distance PGLS", "multivariate regression", "linear regressions", "GLS multiple regression", "PICs", "Multivariate PGLS", "Non-linear regressions", "regression score", "Breush-Pagan")
tests <- multi.gsub(linear, "linear", tests)

@@

## Clean the matchings
tests <- gsub("distance Plinear", "linear", tests)
tests <- gsub("multivariate t_test \\(Hotellings' T\\^2 test\\)", "t_test", tests)
tests <- gsub("Kruskal-Wallis", "anova", tests)

@@

```{r}
## Cleaned data
data <- data[,-c(1,2)]
cleaned_data <- list("data" = data)
cleaned_data$factors <- list(data_taxa = data_taxa_categories, data_type = data_type_categories, full_organism = full_organism_categories, morphospaces = morphospaces_categories, disparity = disparity_categories, tests = tests_categories, phylogeny = phylogeny_categories)

>>>>

## General
general <- c("Metazoans", "Ediacarian", "Marine invertebrates", "Amniotes", "Vertebrates", "Marine ingeneral")
data_taxa <- multi.gsub(general, "general", data_taxa)

@@

## Pairwise distance
pair_distances <- c("DTT \\(morpho evolution in relation to diversification\\)", "DTT pairwise Euclidean distance", "weighted mean pairwise dissimilarity", "pairwise euclidean distance", "DTT pairwise average squared Euclidean distance", "mean pairwise dissimilarity", "sum of squared pairwise distance between coordinates", " pairwise distance", "average pairwise disparity", "Average pairwise squared distance", "average pairwise dissimilarity", "mean square distance between sp", "distance between species", "pairwise character dissimilarity", "mean pairwise distance", "pairwise distance", "mean squared pairwise difference in body size", "average morphological dissimilarity", "Average pairwise dissimilarity", "Pairwise Mahalanobis distance", "sum of the absolute distance for each variable", "DTT pairwise squared distances")
disparity <- multi.gsub(pair_distances, "pair_distances", disparity)

@@

## regressions
regressions <- c("PGLS \\(PC \\~ trait\\)", "Partial Least Squares", "Canonical analysis \\(PCM style\\)", "lm", "Covariance ratio", "GLS", "distance PGLS", "multivariate regression", "linear regressions", "GLS multiple regression", "PICs", "Multivariate PGLS", "Non-linear regressions", "regression score", "Breush-Pagan")
tests <- multi.gsub(regressions, "regressions", tests)

@@

## Clean the matchings
tests <- gsub("distance Plinear", "linear", tests)
tests <- gsub("multivariate t_test \\(Hotellings' T\\^2 test\\)", "t_test", tests)
tests <- gsub("Kruskal-Wallis", "anova", tests)
tests <- gsub("distance Pregressions", "regressions", tests)

@@

```{r}
## Cleaned data
data <- data[,-c(1,2)]
cleaned_data <- list("data" = data)
cleaned_data$factors <- list(data_taxa = data_taxa_categories, data_type = data_type_categories, full_organism = full_organism_categories, morphospaces = morphospaces_categories, disparity = disparity_categories, tests = tests_categories, phylogeny = phylogeny_categories)
cleaned_data$unique_disparity <- number_unique_disparities
